---
title: "Processing"
format: html
execute: 
  echo: false
  warning: false
---

## Purpose

Process scraped data for output.

### Planning

There are three parts.

1. Ingest the data.

2. Filter and join.
2.5 Retry the failed entries

3. Export.

## Ingest

```{r}
library(tidyverse)
library(gt)

files <- list.files(here::here("data", "raw"), pattern = ".rds", full.names = T)

df <- files %>% 
  map_df(read_rds)
```

## Filter and join

Filter and unnest

```{r}
df_not_failed <- df %>% 
  filter(data != "failed")

# df_failed <- df %>% 
#   filter(data == "failed")

df_tab_zero <- df_not_failed %>% 
  unnest(data) %>% 
  unnest() %>% 
  filter(table_number == "Tab 0")

df_tab_not_zero <- df_not_failed %>% 
  unnest(data) %>% 
  unnest() %>% 
  filter(table_number != "Tab 0")

df_tab_zero_unnested <- df_tab_zero %>% 
  unnest()

df_tab_not_zero_unnested <- df_tab_not_zero %>% 
  unnest() %>% 
  unnest()
```

Join

```{r}
df_out <- df_tab_zero_unnested %>% 
  bind_rows(df_tab_not_zero_unnested)

# df_out %>%
#   count(family, title, sort = T)
# 
# df_out %>% 
#   filter(str_detect(title, "Von Schantz nr 1255")) %>% view()
```

## Process

Line breaks.

In some instances, line breaks should be interpreted as new rows. We can use the `separate_rows` command to do this, and then `str_squish` afterwards.

```{r}
df_out %>% 
  filter(str_detect(value, "\n")) %>% head(200) %>% view()

df_out_line_breaks <- df_out %>% 
  separate_rows(value, sep = "\n")
```

Remove family origin from value column. Sometimes the first line in value is the same as the family origin.



```{r}
df_out_line_breaks_filtered <- df_out_line_breaks %>% 
  filter(family_origin != value) %>%
  filter(!value %in% c("", "\n"))

df_out_line_breaks_filtered %>% 
  head(100) %>% view()

df_out_line_breaks_filtered %>% 
  count(title, sort = T) %>% tail(200) %>% view()
```

Remove repeated observations

```{r}
df_out_value_counts <- df_out_line_breaks_filtered %>% 
  group_by(title, table_number) %>% 
  mutate(top_entry = case_when(
    row_number() == 1 ~ value,
    TRUE ~ NA_character_
  )) %>% 
  ungroup()

df_out_deduplicated <- df_out_value_counts %>%
  mutate(flag_up_col = top_entry) %>%
  fill(flag_up_col, .direction = "up") %>%
  group_by(title, table_number) %>%
  mutate(flag_col = case_when(
    row_number() != 1 & flag_up_col == value ~ "TRUE",
    TRUE ~ NA_character_
  )) %>%
  fill(flag_col, .direction = "down") %>%
  ungroup() %>%
  filter(is.na(flag_col)) %>% 
  select(-c(top_entry:flag_col))
  
  
df_out_arranged <- df_out_deduplicated %>% 
  mutate(family_number = parse_number(title),
         table_number = parse_number(table_number)) %>% 
  arrange(family, family_number) %>% 
  select(-family_number)

```


### Export data

```{r}
# library(haven)
df_out_arranged %>% 
  write_excel_csv2(here::here("data", "processed", "adelsvapen_dataset.csv"))


df_out_arranged %>% 
  # select(-value1) %>% 
  write_csv2(here::here("data", "processed", "complete_dataset_pass_1.csv"))
```

